Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-09 mr-review.Rmd
added two new section headers
noted
minor fixes

The approaches to MR can be classified into two categories: two-stage methods and 
likelihood-based methods. Both two-stage strategies and likelihood-based strategies 
make parametric assumptions for the identification of causal effects [@burgess_review_2017].

@@

where the $\epsilon_i$ are assumed to be iid normal random variables with mean zero.

@@

where the $\tau_i$ are assumed to be iid normal random variables with mean zero and $\hat x_i$ denotes the fitted value for $x_i$ obtained from Equation \@ref(eq:lm1).

@@

where $\epsilon$ is assumed to be a vector of iid normal random variables with mean zero.

@@

Horizontal pleiotropy refers to the presence of multiple pathways from a genetic 
variant to the outcome. One of these multiple pathways may contain the exposure variable.
The fact that there are multiple pathways from the genetic variant to the outcome violates
standard MR assumptions. @verbanck_detection_2018 documented widespread horizontal pleiotropy 
in GWAS. This finding motivated the development of MR-PRESSO and inspired 
further research into methods to model and to account for horizontal pleiotropy [@verbanck_detection_2018].

@@

>>>>

Many approaches to MR can be classified into two categories: two-stage methods and 
likelihood-based methods. Both two-stage strategies and likelihood-based strategies 
make parametric assumptions for the identification of causal effects [@burgess_review_2017].

@@

where the $\epsilon_i$ are assumed to be independent and identically distributed normal random variables with mean zero.

@@

where the $\tau_i$ are assumed to be independent and identically distributed  normal random variables with mean zero and $\hat x_i$ denotes the fitted value for $x_i$ obtained from Equation \@ref(eq:lm1).

@@

where $\epsilon$ is assumed to be a vector of independent and identically distributed normal random variables with mean zero.

@@

Horizontal pleiotropy refers to the presence of multiple pathways from a genetic 
variant to the outcome. One of these multiple pathways may contain the exposure variable.
The fact that there are multiple pathways from the genetic variant to the outcome violates
standard MR assumptions. @verbanck_detection_2018 documented widespread horizontal pleiotropy 
in GWAS. This finding motivated the development of MR-PRESSO and inspired 
further research into methods to model horizontal pleiotropy [@verbanck_detection_2018].

@@

# Software

# Non-continuous outcomes

Binary, survival, count - see discussion section of MRAID paper.
